### 2023-05-08 manuscript.tex
; * manuscript.tex: Clean up programming style.

\documentclass[12pt, a4paper]{report}
\usepackage{imakeidx}
\usepackage{setspace}
\usepackage[type={CC},modifier={by-sa},version={4.0}]{doclicense}
\usepackage[margin=1in]{geometry}
\usepackage{lua-widow-control}
\usepackage{microtype}
\usepackage{mathtools}
\usepackage{unicode-math}
\usepackage[style]{abstract}
\usepackage[style=unified]{biblatex}
\usepackage[style=british]{csquotes}
\usepackage{datetime}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{ebproof}
\usepackage{tikz}
\usepackage[linguistics]{forest}
\usepackage{linguex}

@@

\usetikzlibrary{automata}
\tikzset{auto}
\forestset{auto/.style={for root={baseline}, for tree={calign=first}}}

@@

\ex.
\begin{tikzpicture}[baseline=(bow.base)]
  \node[state] at (0,0) (bow) {\(q_{1}\)};
  \node[state,accepting] at (2,1) (noop) {\(q_{2a}\)};
  \node[state] at (4,1) (invalid) {\(q_{3a}\)};
  \node[state] at (2,-1) (write) {\(q_{2b}\)};
  \node[state,accepting] at (4,-1) (valid) {\(q_{3b}\)};
  \path[->]
  (bow) edge [loop left] node {\(\text{?}:\text{?}\)} ()
  (bow) edge node {\(a:a\)} (noop)
  (noop) edge [loop above] node {\(\text{?}:\text{?}\)} ()
  (noop) edge [bend left] node {\(a:a\)} (invalid)
  (invalid) edge [loop above] node {\(\text{?}:\text{?}\)} ()
  (invalid) edge [bend left] node {\(a:a\)} (noop)
  (bow) edge ['] node {\(a:b\)} (write)
  (write) edge [loop below] node {\(\text{?}:\text{?}\)} ()
  (write) edge [bend left] node {\(a:b\)} (valid)
  (valid) edge [loop below] node {\(\text{?}:\text{?}\)} ()
  (valid) edge [bend left] node {\(a:b\)} (write);
\end{tikzpicture}

@@

\ex.
\begin{tikzpicture}[baseline=(loop.base)]
  \node[state,initial,initial text={\(a:a\)}] at (0,0) (loop) {\(a\)};
  \path[->] (loop) edge [loop right] node {\(a:b\)} ();
\end{tikzpicture}

@@

\ex.
\begin{tikzpicture}[baseline=(a.base)]
  \node[state,initial,initial text={\(a:a\)}] at (0,0) (a) {\(a\)};
  \node[state] at (2,0) (b) {\(b\)};
  \path[->]
  (a) edge [bend left] node {\(a:b\)} (b)
  (b) edge [bend left] node {\(a:a\)} (a);
\end{tikzpicture}

>>>>

\documentclass[12pt, a4paper]{report}
\usepackage{imakeidx}
\usepackage{setspace}
\usepackage[type=CC, modifier=by-sa, version=4.0]{doclicense}
\usepackage[margin=1in]{geometry}
\usepackage{lua-widow-control}
\usepackage{microtype}
\usepackage{mathtools}
\usepackage{unicode-math}
\usepackage[style]{abstract}
\usepackage[style=unified]{biblatex}
\usepackage[style=british]{csquotes}
\usepackage{datetime}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{ebproof}
\usepackage{tikz}
\usepackage[linguistics]{forest}
\usepackage{linguex}

@@

\usetikzlibrary{automata}
\tikzset{auto}
\forestset{auto/.style={for root=baseline, for tree={calign=first}}}

@@

\ex.
\begin{tikzpicture}[baseline=(bow.base)]
  \node[state] at (0, 0) (bow) {\(q_{1}\)};
  \node[state, accepting] at (2, 1) (noop) {\(q_{2a}\)};
  \node[state] at (4, 1) (invalid) {\(q_{3a}\)};
  \node[state] at (2, -1) (write) {\(q_{2b}\)};
  \node[state, accepting] at (4, -1) (valid) {\(q_{3b}\)};
  \path[->]
  (bow) edge [loop left] node {\(\text{?}:\text{?}\)} ()
  (bow) edge node {\(a:a\)} (noop)
  (noop) edge [loop above] node {\(\text{?}:\text{?}\)} ()
  (noop) edge [bend left] node {\(a:a\)} (invalid)
  (invalid) edge [loop above] node {\(\text{?}:\text{?}\)} ()
  (invalid) edge [bend left] node {\(a:a\)} (noop)
  (bow) edge ['] node {\(a:b\)} (write)
  (write) edge [loop below] node {\(\text{?}:\text{?}\)} ()
  (write) edge [bend left] node {\(a:b\)} (valid)
  (valid) edge [loop below] node {\(\text{?}:\text{?}\)} ()
  (valid) edge [bend left] node {\(a:b\)} (write);
\end{tikzpicture}

@@

\ex.
\begin{tikzpicture}[baseline=(loop.base), initial text=\(a:a\)]
  \node[state, initial] at (0, 0) (loop) {\(a\)};
  \path[->] (loop) edge [loop right] node {\(a:b\)} ();
\end{tikzpicture}

@@

\ex.
\begin{tikzpicture}[baseline=(a.base), initial text=\(a:a\)]
  \node[state, initial] at (0, 0) (a) {\(a\)};
  \node[state] at (2, 0) (b) {\(b\)};
  \path[->]
  (a) edge [bend left] node {\(a:b\)} (b)
  (b) edge [bend left] node {\(a:a\)} (a);
\end{tikzpicture}
